---
title: "nicfall_originalhwcode_05"
author: "Nicola Kriefall"
date: "11/7/2019"
output: html_document
---

[Hw assignment #5](https://fuzzyatelin.github.io/bioanth-stats/homework-05.html)

1. Using the “KamilarAndCooperData.csv” dataset, run a linear regression looking at log(HomeRange_km2) in relation to log(Body_mass_female_mean) and report your β coeffiecients (slope and intercept).

```{r}
#first, reading in the data:
library(curl)
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN597_Fall19/KamilarAndCooperData.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
str(d$HomeRange_km2) #lots of NAs 
str(d$Body_mass_female_mean) #more NAs
d_km <- d[complete.cases(d$HomeRange_km2),] #removing NAs for home range
d_full <- d_km[complete.cases(d_km$Body_mass_female_mean),] #removing NAs for body mass

#linear regression looking at log(home range) vs. log(body mass female mean)
model <- lm(log(d_full$HomeRange_km2)~log(d_full$Body_mass_female_mean),data=d_full)
#intercept is reportedly -9.441
#slope is reportedly 1.036
```

[2] Then, use bootstrapping to sample from your data 1000 times with replacement, each time fitting the same model and calculating the same coefficients. This generates a sampling distribution for each β coefficient.

```{r}
x <- log(d_full$Body_mass_female_mean)
y <- log(d_full$HomeRange_km2)
set.int <- NULL # sets up a dummy variable to hold our 10000 simulations
for (i in 1:1000){
  bw <- sample(x,size=30,replace=TRUE)
  km <- sample(y,size=30,replace=TRUE)
  lmz <- lm(km~bw)
  set.int[i] <- lmz[["coefficients"]][["(Intercept)"]]
}
set.slope <- NULL # sets up a dummy variable to hold our 10000 simulations
for (i in 1:1000){
  bw <- sample(x,size=30,replace=TRUE)
  km <- sample(y,size=30,replace=TRUE)
  lmz <- lm(km~bw)
  set.slope[i] <- lmz[["coefficients"]][["bw"]]
}
sd(x=set.int)
sd(x=set.slope)

```



Estimate the standard error for each of your β coefficients as the standard deviation of the sampling distribution from your bootstrap and determine the 95% CI for each of your β coefficients based on the appropriate quantiles from your sampling distribution.

How does the former compare to the SE estimated from your entire dataset using the formula for standard error implemented in lm()?

How does the latter compare to the 95% CI estimated from your entire dataset?




